Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-06-06 paper/comoving-followup.tex
remove extra item
tODO about exoplanets

Several of our targets and all of our calibration targets have previously
measured radial velocities (RVs).
We can therefore estimate the absolute velocity uncertainties by comparing our
derived radial velocities with high-quality prior measurements.
Following previous work (\citealt{Shaya:2011}), we search for previous RV
measurements (in decreasing order of priority) with:
\begin{enumerate}
  \item The Geneva-Copenhagen Survey of the Solar Neighborhood
  (\citealt{Nordstrom:2004}).
  \item The Catalogue of Radial Velocities of Galactic Stars with Astrometric
  Data, the Second Version (\citealt{Kharchenko:2007}).
  \item The General Catalogue of Mean Radial Velocities
  (\citealt{Barbier-Brossat:2000}).
  \item The SIMBAD database (\citealt{Wenger:2000}). We use \package{astroquery}
  to retrieve records from the database, which do not contain uncertainties but
  do contain a quality flag. We only retain RVs that have a quality flag set to
  `A' and adopt a $5~\kms$ uncertainty for all such values.
  \item
\end{enumerate}
We find that \todo{XXX} of our target stars have reliable prior measurements,
along with the \todo{YYY} calibration targets.
\figurename~\ref{fig:compare-previous} shows the distribution of velocity
differences between our measurements and literature values.
From this distribution, we compute the MAD and estimate the standard deviation
to be $\approx 20~\kms$, which we adopt as our global systematic error for all
absolute radial velocities.
We note, however, that for computing \emph{relative} velocities for pairs of
nearby stars, it is the RV precision that matters most.

@@

@@

TODO: 10 overlap with Shaya and Olling

TODO: Do I want to do isochrone fitting for all of them?

@@

TODO: Plot of magnitude of 3d velocity difference vs. 3d separation (inferred).

TODO: separation distribution - combine with Shaya and Olling sample!

TODO: distribution of orbital poles in Galactic coordinates

@@

TODO: Orbits of true pairs in the Galaxy, any halo or thick-disk?

>>>>

Several of our targets and all of our calibration targets have previously
measured radial velocities (RVs).
We can therefore estimate the absolute velocity uncertainties by comparing our
derived radial velocities with high-quality prior measurements.
Following previous work (\citealt{Shaya:2011}), we search for previous RV
measurements (in decreasing order of priority) with:
\begin{enumerate}
  \item The Geneva-Copenhagen Survey of the Solar Neighborhood
  (\citealt{Nordstrom:2004}).
  \item The Catalogue of Radial Velocities of Galactic Stars with Astrometric
  Data, the Second Version (\citealt{Kharchenko:2007}).
  \item The General Catalogue of Mean Radial Velocities
  (\citealt{Barbier-Brossat:2000}).
  \item The SIMBAD database (\citealt{Wenger:2000}). We use \package{astroquery}
  to retrieve records from the database, which do not contain uncertainties but
  do contain a quality flag. We only retain RVs that have a quality flag set to
  `A' and adopt a $5~\kms$ uncertainty for all such values.
\end{enumerate}
We find that \todo{XXX} of our target stars have reliable prior measurements,
along with the \todo{YYY} calibration targets.
\figurename~\ref{fig:compare-previous} shows the distribution of velocity
differences between our measurements and literature values.
From this distribution, we compute the MAD and estimate the standard deviation
to be $\approx 20~\kms$, which we adopt as our global systematic error for all
absolute radial velocities.
We note, however, that for computing \emph{relative} velocities for pairs of
nearby stars, it is the RV precision that matters most.

@@

\todo{Cross-match with exoplanets catalog http://exoplanets.org/csv-files/exoplanets.csv}

@@

\todo{10 overlap with Shaya and Olling}

\todo{Do I want to do isochrone fitting for all of them?}

@@

\todo{Plot of magnitude of 3d velocity difference vs. 3d separation (inferred).}

\todo{separation distribution - combine with Shaya and Olling sample!}

\todo{distribution of orbital poles in Galactic coordinates}

@@

\todo{Orbits of true pairs in the Galaxy, any halo or thick-disk?}
